A Catalogue of Twists of Supersymmetric Gauge Theories

### 2020-01-21 paper.tex
6d N=(1, 1)

\chris{Possible topics for the introduction
\begin{enumerate}
 \item  Context and literature on twists, including in the BV formalism.  There's a perspective there in terms of derived algebraic geometry (our mapping stacks we like to talk about).  Also at least a remark on the perspective in terms of coupling to twisted sugra.
 \item  perspective in terms of twisting homomorphisms, and putting twisted theories on curved backgrounds.
 \item  Mathematical literature on SUSY Yang-Mills, including Baez-Huerta and references therein.
 \item  Strategy for computations: coupling to background fields, homotopical SUSY action (reference Baulieu et al), proving the CME is satisfied including the background symmetry fields, then computing the twist in terms of the EOM in a few examples, and computing many other examples via dimensional reduction.
 \item  Table of the twists, and commentary on where each has appeared before in the literature.
 \item  EOM of A-twists, and connection to various PDEs of interest in QFT.
 \item  Connection between twisted BV theories and twisted factorization algebras, and therefore to our earlier paper on $\bb E_n$ algebras.
 \item  Quantization: for cotangent theories and their deformations there's a 1-loop exact prequantization, just need to calculate the 1-loop anomaly to the QME.  In many cases this is worked out.
 \item  Summary of the sections of the paper.
\end{enumerate}}

@@

\subsection*{Acknowledgements}

@@

@@

\subsubsection{Generalized Hodge theory}
Generalized BF theories can be naturally deformed to theories which are perturbatively trivial, but which arise as shadows of non-trivial non-perturbative theories.  These will often appear as topological twists of supersymmetric field theories, the most famous example being the 2d A-model \chris{refer also to the introduction}. By a deformation we will mean a $\CC[t]$-family of classical BV theories which reduce to the given theory at $t=0$.

Given an $L_\infty$ algebra $\fg$ we denote by $\fg_{\Hod}$ the $\CC[t]$-linear $L_\infty$ algebra
\[\fg_{\Hod} = \CC[t]\otimes (\fg\oplus \fg[1])\]
with the $L_\infty$ brackets coming from the $L_\infty$ brackets on $\fg$ in the first term, where we consider $\fg[1]$ as the adjoint representation of $\fg$. The differential is given by the original differential on $\fg$ plus the term $t\id$ from the second summand to the first summand.  The terminology here comes from Simpson's Hodge stack \cite{Simpson}: if $X$ is a smooth scheme, or more generally a derived Artin stack, one can define a derived stack $X_{\mr{Hod}}$ over $\bb A^1$, where the fiber at $0 \in \bb A^1$ is the Dolbeault stack $X_{\mr{Dol}}$ of $X$, essentially the 1-shifted tangent bundle, and the fiber at a non-zero point is equivalent to the de Rham stack $X_{\mr{dR}}$ of $X$, which has contractible tangent complex.

If $\fg$ carries a nondegenerate invariant symmetric pairing of degree $d$, so does $\fg_{\Hod}$.

\begin{definition} \label{Hodge_family_def}
Let $X$ and $Y$ be complex manifolds and $M$ a smooth oriented manifold. Fix an $L_\infty$ algebra $\fg$. We assume $X$ is equipped with a holomorphic volume form $\Omega_X \in\Omega^{\dim(X), 0}(X)$ and $\fg$ is equipped with a nondegenerate invariant symmetric pairing $\langle-, -\rangle\colon \fg\otimes\fg\rightarrow \CC[\dim_\CC(X) + 2\dim_\CC(Y) + \dim(M) - 3]$. The \defterm{generalized Hodge theory} is the $\CC[t]$-linear classical BV theory given by the generalized Chern--Simons theory with the space of fields $\map(X\times Y_{\mr{Dol}}\times M_{\mr{dR}}, B \fg_\Hod)$.
\end{definition}

@@

The specialization of the generalized Hodge theory at $t\neq 0$ is perturbatively trivial.
\label{prop:Hodgetheoryspecialization}
\end{prop}

\begin{proof}
At $t=0$ we get
\[\left.\fg_\Hod\right|_{t=0}\cong \fg\oplus \fg[1]\cong \fg\oplus \fg^*[d-1],\]
where we use the symmetric bilinear pairing on $\fg$ in the second isomorphism. The first claim then follows from Example \ref{ex:CSBF}.

@@

@@

\item (\textbf{6d $\mc N=(1, 0)$ supersymmetry}) $A=\mathbb{H}\otimes_{\RR}\CC\cong \eend(W_+)$, where $W_+$ is a two-dimensional symplectic vector space with $\sigma$ given by the dual operator. Moreover, $\dim(V) = 6$ and $\Sigma = S_+\oplus W_+$.

@@

Let $V_\RR = \RR^8$ and $V=V_\RR\otimes_\RR\CC$. Fix a K\"ahler structure on $\RR^8$ and denote by $L\subset V$ the $i$-eigenspace of the complex structure. Moreover, fix a complex volume form on $L$. Under $\SU(L)\subset \Spin(V)$ the semi-spin representation $S_+$ decomposes as
\[S_+\cong \CC \alpha\oplus \wedge^2 L\oplus \CC \beta.\]
The scalar spinorial pairing $S_+\otimes S_+\rightarrow \CC$ is given by pairing the outer terms with each other and $\wedge^2L$ with itself using the complex volume form on $L$. Consider a family of square-zero supercharges
\begin{equation}
Q_t = \alpha + t\beta\in\Sigma_+
\label{eq:8dHodgefamily}
\end{equation}
for $t\in\CC$. We have
\[(Q_t, Q_t) = t,\]
so at $t=0$ we have a holomorphic supercharge and and $t\neq 0$ we have a topological supercharge.

@@

\item Square-zero supercharges $Q$ of rank 2. These have 5 invariant directions and do not admit a compatible homomorphism $\alpha$, so they give rise to a $\ZZ/2\ZZ$-graded theory.
\end{itemize}

@@

\begin{thm}
The twist of 7d $\cN=1$ super Yang--Mills with respect to the family $Q_t$ of square-zero supercharges is perturbatively equivalent to the generalized Hodge theory $\map(\CC^3\times \RR_{\mr{dR}}, B\fg_{\Hod})$. Moreover, this equivalence is $\SU(3)$-equivariant.
\end{thm}
\begin{proof}
The family of square-zero supercharges given by equation \eqref{eq:7dHodgefamily} may be obtained by dimensional reduction of the corresponding family $Q_t^8$ (see equation \eqref{eq:8dHodgefamily}) in 8 dimensions. The twist of 7d $\cN=1$ super Yang--Mills with respect to $Q_t$ is obtained by dimensional reduction of the twist of 8d $\cN=1$ super Yang--Mills with respect to $Q_t^8$. The claim then follows from Theorem \ref{thm:8dHodgetwist} and Corollary \ref{cor:Hodgeholomorphicreduction}.
\end{proof}

@@

Let $\omega\in\Omega^{1, 1}(M)$ be the K\"ahler form, $\Omega\in\Omega^{3, 0}(M)$ the holomorphic volume form and $\ol{\Omega}\in\Omega^{0, 3}(M)$ the antiholomorphic volume form.  We denote the real volume form on $M$ by
\[\dvol = \frac{\omega^3}{6} = \Omega\wedge \ol{\Omega}.\]

@@

If $U=T^*R=R\oplus R^*$, the R-symmetry group is enhanced to $G_R=\SU(2)\times \U(1)$. We have a homomorphism $\alpha\colon \U(1)\hookrightarrow G_R=\SU(2)\times \U(1)$ given by the diagonal embedding which is compatible with the holomorphic supercharge. We may also use a different twisting homomorphism
\[\phi\colon\MU(3)\xrightarrow{\det^{1/2}}\U(1)\xrightarrow{\alpha} G_R.\]

@@

\subsection{\texorpdfstring{$\mc N = (1,1)$}{N=(1,1)} Super Yang-Mills Theory}

There is a 6d gauge theory with $\mc N=(1,1)$ supersymmetry obtained by dimensionally reducing the maximal super Yang-Mills theory on $\RR^{10}$ down to $\RR^6$. This theory is alternatively obtained by considering the $\mc N=(1,0)$ theory above with representation $U = T^*\gg$: the $\mc N=(1,0)$ supersymmetry algebra action can be promoted to an $\mc N=(1,1)$ supersymmetry action.

\vspace{-10pt}
\paragraph{Fields:} Let us write the BRST fields in $\mc N=(1,1)$ super Yang Mills theory on $\RR^6$ as $c$, the ghost, along with:
\begin{itemize}
 \item Bosons: a gauge field $A$, along with 4 scalars $\{\phi_i\}$.  These transform in the vector representation of the R-symmetry group $\Spin(4)_R$, i.e. the tensor product $W_+ \otimes W_-$ of the two fundamental representations of $\Sp(W_+) \times \Sp(W_-)$.  We'll write just $\phi$ for the scalars, viewed as a section of the trivial $W_+ \otimes W_-$-bundle on $\RR^6$.
 \item Fermions: spinor fields $\lambda^+ \otimes u^+$ and $\lambda^- \otimes u^-$ valued in $S_+ \otimes W_+$ and $S_- \otimes W_-$ respectively.
\end{itemize}

We can write the supersymmetry action here explicitly. \chris{though it isn't necessary: remove it?}

\begin{prop} \label{O6_decomposition_of_susy_prop}
After reduction to $\mr O(6)$, the interaction terms $I^{(1)}$ and $I^{(2)}$ become
\begin{align*}
I^{(1)}(Q^+) &= \langle A^\vee, \Gamma(Q^+, \lambda^+)\rangle\omega(w^+,u^+) + \langle \phi^\vee, (Q^+,\lambda^-)\rangle w^+ \otimes u^- + \\&\qquad + \langle (\lambda^{+} \otimes u^+)^\vee, \sd F_A (Q^+ \otimes w^+) \rangle + \langle (\lambda^{-} \otimes u^-)^\vee, \rho(\dd \phi)(Q^+ \otimes w^+) \rangle\\
I^{(2)}(Q^+, Q^+) &= \left(\langle\lambda^{+\vee},Q^+\rangle\langle u^{+\vee}, w^+ \rangle\right)^2
\end{align*}
if $Q^+ \otimes w^+$ is an element of $S_+ \otimes W_+$, and
\begin{align*}
I^{(1)}(Q^-) &= \langle A^\vee, \Gamma(Q^-, \lambda^-)\rangle\omega(w^-,u^-) + \langle \phi^\vee, (Q^-,\lambda^+)\rangle w^- \otimes u^+ + \\&\qquad + \langle (\lambda^{-} \otimes u^-)^\vee, \sd F_A (Q^- \otimes w^-) \rangle + \langle (\lambda^{+} \otimes u^+)^\vee, \rho(\dd \phi)(Q^- \otimes w^-) \rangle\\
I^{(2)}(Q^-, Q^-) &= \left(\langle\lambda^{-\vee},Q^-\rangle\langle u^{-\vee}, w^- \rangle\right)^2
\end{align*}
if $Q^- \otimes W_-$ is an element of $S_- \otimes W_-$.  In each of these expressions, we have suppressed in the notation some contractions of tensors between $W_+ \otimes W_-$ and its dual.  There is an additional term in $I^{(2)}$ associated to the action of a rank $(1,1)$ supercharge $Q^+ + Q^-$, which takes the form
\[I^{(2)}(Q^+, Q^-) = (\lambda^{+\vee}, \lambda^{-\vee})(Q^+,Q^-) \langle u^{+\vee} \otimes u^{-\vee}, w^+ \otimes w^-\rangle + \langle c^\vee, \phi \rangle(Q^+,Q^-) w^+ \otimes w^-. \]
\end{prop}

\begin{remark}
If we set $\lambda^- \otimes u^-$ and $\phi$ to zero, and consider only the action of $Q^+ \otimes w^+$, then we recover the supersymmetry action for the $\mc N=(1,0)$ pure gauge theory.  If instead we set $\lambda^+ \otimes u^+$ and $A$ to zero, and consider only the action of $Q^- \otimes w^-$ then we recover the supersymmetry action for the $\mc N=(1,0)$ pure matter theory.
\end{remark}

\vspace{-10pt}
\paragraph{Twisting data:}
In the 6 dimensional $\mc N=(1,1)$ supersymmetry algebra, there are now 4 classes of inequivalent non-zero supercharges by which we can twist.
\begin{enumerate}
 \item Rank $(1,0)$ spinors, $Q^+ \otimes w^+$.  These automatically square to zero, and are holomorphic.  Such supercharges factor through a copy of the $\mc N=(1,0)$ supersymmetry algebra.
 \item Rank $(1,1)$ spinors, $Q = Q^+ \otimes w^+ + Q^- \otimes w^-$.  These automatically square to zero, and split into two inequivalent classes:
 \begin{enumerate}
 \item Generically, $Q$ is topological.
 \item There is a degenerate locus where $Q$ has 4 invariant directions.  The former class can be realised as a degeneration of this case.
 \end{enumerate}
 \item Rank $(2,2)$ square-zero spinors.  These supercharges have 5-dimensional image in $\CC^6$.  The corresponding twists are only $\ZZ/2\ZZ$-graded.
\end{enumerate}

We already considered the holomorphic twist in the previous section: it admits the following description.

\begin{theorem} \label{6d_holo_twist_thm}
The holomorphic twist of 6d $\mc N=(1,1)$ super Yang-Mills theory is perturbatively equivalent to holomorphic BF theory on $\CC^3$ with target given by the adjoint quotient $\gg/\gg$, i.e. the theory with fields $T^*[-1]\mr{Map}(\CC^3, \gg/\gg)$.
\end{theorem}

\begin{proof}
Take the description of the holomorphically twisted theory from Theorem \ref{thm:6dholomorphictwist}, and let $U = T^*\gg$.  One identifies the resulting description as a $\ZZ$-graded theory with a cotangent theory as described in Remark \ref{6d_BF_remark}.
\end{proof}

The remaining three classes of twists are new: they all arise via appropriate dimensional reductions from twists of 7d $\mc N=1$ super Yang-Mills.

\begin{theorem} \label{6d_rk11_twist_thm}
The twist of 6d $\mc N=(1,1)$ super Yang-Mills theory by a rank $(1,1)$ supercharge with 4 invariant directions on the product of a Calabi-Yau surface $S$ and an oriented 2-manifold $\Sigma$ is perturbatively equivalent to mixed BF theory on the product $S \times \Sigma_{\mr{dR}}$. This twist degenerates to a one-parameter family of topological twists of the form $\map(S \times \Sigma_{\mr{dR}}, B\gg)_{\mr{Hod}}$.
\end{theorem}

\begin{proof}
We obtain this description by starting with the 1-parameter family of twisted theories from Theorem \ref{7d_holo_twist_thm}, and dimensionally reducing along one of the Calabi-Yau directions.  That is, by applying Proposition \ref{CS_diml_red_prop} to the family of twists in 7-dimensions.
\end{proof}

\begin{theorem} \label{6d_rk22_twist_thm}
The twist by a rank $(2,2)$ supercharge of 6d $\mc N=(1,1)$ super Yang-Mills theory on the product of a Calabi-Yau curve $C$ with an oriented 4-manifold $M_4$ is perturbatively equivalent to mixed Chern-Simons theory on $C \times (M_4)_{\mr{dR}}$.
\end{theorem}

\begin{proof}
We now start with the twisted theory from Theorem \ref{7d_rank2_twist_thm}, with 5 invariant directions, and we dimensionally reduce in an de Rham direction.  That is, we apply Proposition \ref{CS_to_BF_diml_red_prop}.
\end{proof}

@@

\begin{theorem}
\chris{Rank $(1,1)$ deforming to rank $(2,1)$, the former is done above, the deformation doesn't come from dimensional reduction.  However, we know how $(1,0)$ deforms to $(2,0)$ (further supercharge acts by the differential operator $\dd_2$), so apply the same deformation to $(1,1)$.} $\mr{Map}(\CC_{\mr{Dol}} \times \RR^2_{\mr{dR}}, B\gg_{\mr{Hod}})$.
\end{theorem}

>>>>

@@

@@

Generalized BF theories can be naturally deformed to theories which are perturbatively trivial, but which arise as shadows of non-trivial non-perturbative theories.  These will often appear as topological twists of supersymmetric field theories, the most famous example being the 2d A-model \chris{refer also to the introduction}.  In order to remain within the world of perturbation theory, we will study these theories as deformations families parameterized by a complex parameter $t$.  So at $t=0$ we will recover generalized BF theory.

We will refer to these families as Hodge deformations of generalized BF theory.  The terminology here comes from Simpson's Hodge stack \cite{Simpson}: if $X$ is a smooth scheme, or more generally a derived Artin stack, one can define a derived stack $X_{\mr{Hod}}$ over $\bb A^1$, where the fiber at $0 \in \bb A^1$ is the Dolbeault stack $X_{\mr{Dol}}$ of $X$, essentially the 1-shifted tangent bundle, and the fiber at a non-zero point is equivalent to the de Rham stack $X_{\mr{dR}}$ of $X$, which has contractible tangent complex.

\begin{definition} \label{Hodge_family_def}
Consider the generalized BF theory on $X \times Y \times M$ associated to the $L_\infty$ algebra $\fg$, and supposed $\fg$ is equipped with a non-degenerate pairing.  The \emph{Hodge deformation} of this generalized BF theory is the $\CC[t]$ family of classical BV theories on $X \times Y \times M$, with $(E_t, \omega_t, I_t) = (E_{\mr{BF}}, \omega_{\mr{BF}}, I_{\mr{BF}})$ the same data as for generalized BF theory, so 
\[E_t = \left(\Omega^{0,\bu}_X \otimes \Omega^{\bu,\bu}_Y \otimes \Omega^\bu_M \otimes \fg[1] \right)\oplus \left(\Omega^{\dim(X),\bu}_X \otimes \Omega^{\bu,\bu}_Y \otimes \Omega^\bu_M\otimes \fg^*\right),\]
but $Q_{\mr{BV},t} = Q_{\text{BV,BF}} + tQ'$, where $Q'$ is the isomorphism
\[Q' \colon \Omega^{0,\bu}_X \otimes \Omega^{\bu,\bu}_Y \otimes \Omega^\bu_M \otimes \fg[1] \to 
\Omega^{\dim(X),\bu}_X \otimes \Omega^{\bu,\bu}_Y \otimes \Omega^\bu_M\otimes \fg^*\]
induced by the Calabi-Yau structure on $X$ and the non-degenerate pairing on $\fg$. 
\end{definition}

Using our mapping stack terminology, we will refer to the Hodge deformation of generalized BF theory as
\[\mr{Map}(X \times Y_{\mr{Dol}} \times M_{\mr{dR}}, B\gg_{\mr{Hod}}).\]

@@

\subsubsection{Generalized Hodge theory}

We will also consider deformations of the generalized BF theory to a perturbatively trivial theory. By a deformation we will mean a $\CC[t]$-family of classical BV theories which reduce to the given theory at $t=0$.

Given an $L_\infty$ algebra $\fg$ we denote by $\fg_{\Hod}$ the $\CC[t]$-linear $L_\infty$ algebra
\[\fg_{\Hod} = \CC[t]\otimes (\fg\oplus \fg[1])\]
with the $L_\infty$ brackets coming from the $L_\infty$ brackets on $\fg$ in the first term, where we consider $\fg[1]$ as the adjoint representation of $\fg$. The differential is given by the original differential on $\fg$ plus the term $t\id$ from the second summand to the first summand.

If $\fg$ carries a nondegenerate invariant symmetric paiirng of degree $d$, so does $\fg_{\Hod}$.

\begin{definition}
Let $X$ and $Y$ be complex manifolds and $M$ a smooth oriented manifold. Fix an $L_\infty$ algebra $\fg$. We assume $X$ is equipped with a holomorphic volume form $\Omega_X \in\Omega^{\dim(X), 0}(X)$ and $\fg$ is equipped with a nondegenerate invariant symmetric pairing $\langle-, -\rangle\colon \fg\otimes\fg\rightarrow \CC[\dim_\CC(X) + 2\dim_\CC(Y) + \dim(M) - 3]$. The \defterm{generalized Hodge theory} is the $\CC[t]$-linear classical BV theory given by the generalized Chern--Simons theory with the space of fields $\map(X\times Y_{\mr{Dol}}\times M_{\mr{dR}}, B \fg_\Hod)$.
\end{definition}

@@

The specialization of the generalized Hodge theory at $t\neq 0$ is perturbatively trivial.
\label{prop:Hodgetheoryspecialization}
\end{prop}
\begin{proof}
At $t=0$ we get
\[\left.\fg_\Hod\right|_{t=0}\cong \fg\oplus \fg[1]\cong \fg\oplus \fg^*[d-1],\]
where we use the symmetric bilinear pairing on $\fg$ in the second isomorphism. The first claim then follows from Example \ref{ex:CSBF}.

@@

\begin{cor}
Let $X, Y, M, \fg$ be as before. Consider the generalized Hodge theory
\[\map(X\times Y_{\mr{Dol}}\times (M\times\RR)_{\mr{dR}}, B\fg_\Hod).\]
Its dimensional reduction along the projection $p\colon X\times Y\times (M\times \RR)\rightarrow X\times Y\times M$ is isomorphic to the generalized Hodge theory
\[\map(X\times Y_{\mr{Dol}}\times M_{\mr{dR}}, T^*[\dim_\CC(X) + 2\dim_\CC(Y) + \dim(M) - 1] B\fg_\Hod).\]
\label{cor:Hodgetopologicalreduction}
\end{cor}

@@

\item (\textbf{6d $\mc N=(1, 0)$ supersymmetry}) $A=\mathbb{H}\otimes_{\RR}\CC\cong \eend(W_+)$, where $W_+$ is a two-dimensional symplectic vector space with $\sigma$ given by the dual operator. Moreover, $\dim(V) = 6$ and $\Sigma = S_+\otimes W_+$.

@@

Let $V_\RR = \RR^8$ and $V=V_\RR\otimes_\RR\CC$. Fix a K\"ahler structure on $\RR^8$ and denote by $L\subset V$ the $i$-eigenspace of the complex structure. Moreover, fix a complex volume form on $L$. Under $\SU(L)\subset \Spin(V)$ the semi-spin representation $S_+$ decomposes as
\[S_+\cong \CC \alpha\oplus \wedge^2 L\oplus \CC \beta.\]
The scalar spinorial pairing $S_+\otimes S_+\rightarrow \CC$ is given by pairing the outer terms with each other and $\wedge^2L$ with itself using the complex volume form on $L$. Consider a family of square-zero supercharges
\begin{equation}
Q_t = \alpha + t\beta\in S_+
\label{eq:8dHodgefamily}
\end{equation}
for $t\in\CC$. We have
\[(Q_t, Q_t) = t,\]
so at $t=0$ we have a holomorphic supercharge and and $t\neq 0$ we have a topological supercharge.

@@

\item Square-zero supercharges $Q$ of rank 2. These have 5 invariant directions and do not admit a compatible homomorphism $\alpha$, so they give rise to a $\ZZ/2\ZZ$-graded theory. We have a twisting homomorphism $\phi\colon \SU(2)\times \Spin(3, \RR)\rightarrow G_R=\Spin(3, \RR)$ given by projection on the second factor, so tht theory carries an action of $\SU(2)\times\Spin(3, \RR)$.
\end{itemize}

@@

\begin{thm}
The twist of 7d $\cN=1$ super Yang--Mills with respect to the family $Q_t$ of square-zero supercharges is perturbatively equivalent to the generalized Hodge theory $\map(\CC^3\times \RR_{\mr{dR}}, B\fg_{\Hod})$. Moreover, this equivalence is $\SU(3)$-equivariant.
\label{thm:7dHodgetwist}
\end{thm}
\begin{proof}
The family of square-zero supercharges given by equation \eqref{eq:7dHodgefamily} may be obtained by dimensional reduction of the corresponding family $Q_t^8$ (see equation \eqref{eq:8dHodgefamily}) in 8 dimensions. The twist of 7d $\cN=1$ super Yang--Mills with respect to $Q_t$ is obtained by dimensional reduction of the twist of 8d $\cN=1$ super Yang--Mills with respect to $Q_t^8$. The claim then follows from Theorem \ref{thm:8dHodgetwist} and Corollary \ref{cor:Hodgeholomorphicreduction}.
\end{proof}

@@

Let $\omega\in\Omega^{1, 1}(M)$ be the K\"ahler form. We denote the real volume form on $M$ by
\[\dvol = \frac{\omega^3}{6}.\]

@@

If $U=T^*R=R\oplus R^*$, the R-symmetry group is enhanced to $G_R=\SU(2)\times \U(1)$. We have a homomorphism $\alpha\colon \U(1)\hookrightarrow G_R=\SU(2)\times \U(1)$ given by the diagonal embedding which is compatible with the holomorphic supercharge. We may also use a new twisting homomorphism
\[\phi\colon\MU(3)\xrightarrow{\det^{1/2}}\U(1)\xrightarrow{\alpha} G_R.\]

@@

The 6d $\cN=(1, 1)$ super Yang--Mills theory is obtained by dimensional reduction from the 10d $\cN=(1, 0)$ super Yang--Mills. It admits $R$-symmetry group $G_R=\Spin(4, \RR)$ under which $W_+, W_-$ are the two semi-spin representations.

Given an element $Q\in S_+\otimes W_+\oplus S_-\otimes W_-$ we denote by $W^*_{Q_\pm}\subset S_\pm$ the images of $Q$. We classify square-zero supercharges according to the ranks of these spaces:
\begin{itemize}
\item Rank $(1, 0)$ and $(0, 1)$. These automatically square to zero and are holomorphic.  Such supercharges factor through a copy of the $\mc N=(1,0)$ (respectively, $\cN=(0, 1)$) supersymmetry algebra. They admit a twisting homomorphism from $\MU(3)$ and a $\ZZ$-grading $\alpha\colon \U(1)\rightarrow G_R$.

\item Rank $(1, 1)$ and $\langle W^*_{Q_+}, W^*_{Q_-}\rangle = 0$. These automatically square to zero and have 4 invariant directions. There is a $\ZZ$-grading $\alpha\colon \U(1)\hookrightarrow G_R=\SU(2)\times \SU(2)$ given by the diagonal embedding and these admit a twisting homomorphism $\phi\colon \MU(2)\times \Spin(2, \RR)\xrightarrow{\det^{1/2}\times \id}\U(1)\xrightarrow{\alpha} G_R$.

\item Rank $(1, 1)$ and $\langle W^*_{Q_+}, W^*_{Q_-}\rangle \neq 0$. These automatically square to zero and are topological. Such supercharges are stabilized by $\SU(3)\subset \Spin(6, \CC)$ and have a $\ZZ$-grading $\alpha\colon \U(1)\rightarrow G_R=\SU(2)\times \SU(2)$ given by the diagonal embedding.

\item Rank $(2, 2)$. The square-zero supercharges have 5 invariant directions and give rise to a $\ZZ/2$-graded theory. There is the identity twisting homomorphism $\phi\colon \Spin(4, \RR)\rightarrow G_R=\Spin(4, \RR)$, so the twisted theory carries a $\Spin(4, \RR)$-action.
\end{itemize}

The 6d $\cN=(1, 1)$ super Yang--Mills theory viewed as a $\cN=(1, 0)$ supersymmetric theory coincides with the 6d $\cN=(1, 0)$ super Yang--Mills with matter in the representation $U=T^*\fg=\fg\oplus \fg^*$. Under this isomorphism the R-symmetry group $\SU(2)\times \U(1)$ of 6d $\cN=(1, 0)$ super Yang--Mills is a subgroup of the R-symmetry group $\SU(2)\times \SU(2)$ of 6d $\cN=(1, 1)$ super Yang--Mills. In particular, from Theorem \ref{thm:6dholomorphictwistgraded} we obtain the following statement.

\begin{thm}
The holomorphic twist of 6d $\cN=(1, 1)$ super Yang--Mills on $M=\RR^6$ is perturbatively equivalent to the holomorphic BF theory on $M\cong \CC^3$ with the space of fields $\map(M, T^*[2] (\fg/\fg))$. Moreover, the equivalence is $\U(3)$-equivariant.
\label{thm:6d11holomorphictwist}
\end{thm}

\subsubsection{Rank $(1, 1)$ partially topological twist}

We define $\alpha$ to be the diagonal embedding $\U(1)\hookrightarrow G_R=\SU(2)\times \SU(2)$ and the twisting homomorphism $\phi$ to be given by the composite
\[\phi\colon \MU(2)\times \Spin(2)\xrightarrow{\det^{1/2}\times \id} \U(1)\xrightarrow{\alpha}G_R.\]

Let $L=\CC^2$ equipped with a Hermitian structure and consider the 7-dimensional spacetime $V^7_\RR = L\times \RR^3$ and the 6-dimensional spacetime $V^6_\RR=L\times \RR^2$. Under the projection $V^7_\RR\rightarrow V^6_\RR$ a rank 2 square-zero supercharge $Q$ in 7 dimensions dimensionally reduces to a rank $(1, 1)$ partially topological square-zero supercharge in 6 dimensions.

\begin{thm}
The rank $(1, 1)$ partially topological twist of 6d $\cN=(1, 1)$ super Yang--Mills is perturbatively equivalent to the generalized BF theory with the space of fields $\map(\CC^2\times \RR^2_{\mathrm{dR}}, T^*[4] B\fg)$. Moreover, the equivalence is $\MU(2)\times\Spin(2, \RR)$-equivariant.
\end{thm}
\begin{proof}
The claim about the underlying $\ZZ/2$-graded theories follows by dimensional reduction (Proposition \ref{CS_diml_red_prop}) along $V^7_\RR\rightarrow V^6_\RR$ from the corresponding statement for the 7-dimensional super Yang--Mills given by Theorem \ref{thm:7dpartiallytopologicaltwist}.

To check that the $\ZZ$-gradings are compatible, we observe that $\alpha$ defined above coincides with $\alpha$ defined for 6d $\cN=(1, 0)$ super Yang--Mills with matter valued in a $\fg$-representation $U=T^*\fg$. In particular, the $\ZZ$-grading of fields in this twist coincides with the $\ZZ$-grading of fields in the holomorphic twist given in Theorem \ref{thm:6dholomorphictwistgraded}. The claim then follows from a direct comparison.
\end{proof}

Next we study the rank $(1, 1)$ topological twist. Let $L=\CC^3$ equipped with a Hermitian structure and consider the spacetime $V_\RR=L$. Under $\SU(L)\subset \Spin(V_\RR)$ the semi-spin representations decompose as
\[
S_+\cong \CC\alpha\oplus L,\qquad S_-\cong \CC\beta\oplus L^*.
\]
Consider a family of square-zero supercharges
\begin{equation}
Q_t = \alpha + t\beta\in \Sigma.
\label{eq:6dHodgefamily}
\end{equation}
At $t=0$ we obtain a rank $(1, 0)$ holomorphic supercharge and at $t\neq 0$ we obtain a rank $(1, 1)$ topological supercharge.

\begin{thm}
The twist of 6d $\cN=(1, 1)$ super Yang--Mills with respect to the family $Q_t$ of square-zero supercharges is perturbatively equivalent to the generalized Hodge theory $\map(\CC^3, T^*[2] B\fg_{\Hod})$. Moreover, this equivalence is $\SU(3)$-equivariant.
\label{thm:6dHodgetwist}
\end{thm}
\begin{proof}
The family of square-zero supercharges given by equation \eqref{eq:6dHodgefamily} lifts to the family of square-zero supercharges in 7 dimensions given by equation \eqref{eq:7dHodgefamily}. So, the twist of 6d $\cN=(1, 1)$ super Yang--Mills is obtained by a dimensional reduction of the twist of 7d $\cN=1$ super Yang--Mills. Therefore, the claim follows from Theorem \ref{thm:7dHodgetwist} and Corollary \ref{cor:Hodgetopologicalreduction}.
\end{proof}

\begin{cor}
The topological twist of 6d $\cN=(1, 1)$ super Yang--Mills is perturbatively trivial.
\end{cor}

\subsubsection{Rank $(2, 2)$ twist}

We finally consider twist by a rank $(2, 2)$ square-zero supercharge $Q\in\Sigma$.

\begin{thm}
The rank $(2, 2)$ twist of 6d $\cN=(1, 1)$ super Yang--Mills is perturbatively equivalent to the generalized Chern--Simons theory with the space of fields $\map(\CC\times \RR^4_{\mr{dR}}, B\fg)$. Moreover, the equivalence is $\Spin(4, \RR)$-equivariant.
\label{thm:6drank22}
\end{thm}
\begin{proof}
Consider the $\Spin(8, \CC)$ semi-spin representations $S^8_\pm$. Under the embedding $\Spin(6, \CC)\times \Spin(2, \CC)\subset \Spin(8, \CC)$, these decompose as
\[S^8_+ = S^6_+\otimes S^2_+\oplus S^6_-\otimes S^2_-,\qquad S^8_- = S^6_+\otimes S^2_-\oplus S^6_-\otimes S^2_+,\]
where $S^6_{\pm}$ are the semi-spin representations of $\Spin(6, \CC)$ and $S^2_{\pm}$ are the semi-spin representations of $\Spin(2, \CC)$. The odd part of the supersymmetry algebra is
\[\Sigma = S^8_+\oplus S^8_-\cong S^6_+\otimes W_+\oplus S^6_-\otimes W_-,\]
where $W_{\pm}\cong S^2_+\oplus S^2_-$. Let $\alpha_\pm$ be basis vectors of $S^2_{\pm}$ and consider an arbitrary supercharge
\[Q = s_+^+\otimes \alpha_+ + s_+^-\otimes \alpha_- + s_-^+\otimes \alpha_- + s_-^-\otimes \alpha_+\in\Sigma,\]
where the lower index on $s$ refers to $S^8_\pm$ and the upper index on $s$ refers to $S^6_\pm$.

Let us assume that $Q$ is a rank $(2, 2)$ supercharge, i.e. $s_+^\pm, s_-^\pm$ are all nonzero. The supercharge $Q$ squares to zero in 6d iff $s_+^+\wedge s_-^+$ under the isomorphism $\wedge^2 S^6_+\cong V$ is equal to $s_+^-\wedge s_-^-$ under the isomorphism $\wedge^2 S^6_-\cong V$.

$Q$ squares to zero in 8d iff it squares to zero in 6d and $(s_+^+, s_-^-) = (s_-^+, s_+^-) = 0$, where $(-, -)$ denotes the natural pairing between $S^6_+$ and $S^6_-\cong (S^6_+)^*$. But by \cite[Lemma 4.42]{ElliottSafronov} the condition that $Q$ squares to zero in 6d already implies the vanishing of these pairings.

So, any square-zero rank $(2, 2)$ supercharge in 6d lifts to a square-zero rank $(1, 1)$ supercharge in 8d and hence by Theorem \ref{thm:8dpartiallytopologicaltwist} they are obtained by a dimensional reduction of a square-zero supercharge in 10d along $(\id\times \Re)\colon \RR^2\times \CC^4\rightarrow \RR^2\times \RR^4$. The statement therefore follows from Theorem \ref{thm:10dCSreduction}.
\end{proof}

@@

\begin{theorem}
\chris{Rank $(1,1)$ deforming to rank $(2,1)$, the former is done above, the deformation maybe doesn't come from dimensional reduction?} $\mr{Map}(\CC_{\mr{Dol}} \times \RR^2_{\mr{dR}}, B\gg_{\mr{Hod}})$.
\end{theorem}
